---
title: "p8106_hw6_jy2965"
author: "Jun Yin"
date: "11/25/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mgcv)
library(modelr)
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```




## Load in data

```{r, message=FALSE}
child_growth = read_csv("./data/birthweight.csv")
skimr::skim(child_growth)
```

* there is no missing

### Tidy data

```{r, message=FALSE}
child_growth_clean = 
child_growth %>% 
  mutate(
    babysex = recode_factor(babysex, `1` = "male", `2` = "female"),
    frace = recode_factor(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    mrace = recode_factor(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"),
    malform = recode_factor(malform, `0` = "absent", `1` = "present"),
    bwt = bwt * 0.0022
  )
```

* There is no missing data in the dataset. Categorical variables were transfered to factor from numeric. 

## Building My own model

```{r}
child_growth_clean = 
  child_growth_clean %>% 
  mutate(
    babysex = fct_infreq(babysex)
  )
mymodel = lm(bwt ~ babysex+blength + delwt + fincome + gaweeks, data = child_growth_clean)
mymodel %>% 
  broom::glance() %>% view
mymodel %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
plots = 
child_growth_clean %>% 
  modelr::add_residuals(mymodel) %>% 
  modelr::add_predictions(mymodel) %>% 
  ggplot(aes(x = pred, y =  resid)) + geom_point() + 
  labs(
    x = "prediction",
    y = "residuals",
    title =  "prediction and residuals"
  )
plots
```

* I chose the potential factors that underly birthweight: `babysex`, `blength`, `delwt`, `fincome`, `gaweeks`. baby sex and baby's length will affect the weight of newborns in an obvious way. Also family's income level will affect the mother's health condition and newborn's nutrition condition, then will cause the difference on newborns' weights. Also, less gastational age will lead to higher possibilities to lighter babies since baby grow in mother's body. 



### Comparison

```{r, message=FALSE}
cv_df = 
  crossv_mc(child_growth_clean, 100)
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
cv_df = 
  cv_df %>% 
  mutate(
    mymodel = map(train, ~lm(bwt ~ babysex + blength + delwt + fincome + gaweeks, data = .x)),
    maineffect = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    threewayinteraction = map(train,~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mymodel = map2_dbl(mymodel, test, ~rmse(model = .x, data = .y)),
    rmse_maineffect = map2_dbl(maineffect, test, ~rmse(model = .x, data = .y)),
    rmse_threewayinteraction = map2_dbl(threewayinteraction, test, ~rmse(model = .x, data = .y))
    )
comparison_plot =
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse", 
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
    title = "model comparison"
  )
comparison_plot
```


## Question 2

### load in data
```{r, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## clean 
```{r}
weather_df_clean =
weather_df %>% 
  select(tmax, tmin)
```




